
%\newglossaryentry{html}
%{ name=HTML, description={Hypertext Markup Language is the backbone of webpages.  Static pages are simply served up by the webserver on request.  Dynamic pages are created and returned by the webserver on the fly.},
%}



%\newglossaryentry{css}
%{  name=CSS, description={Cascading Style Sheets are a way to apply styling to web-pages. It can be inline, or through an external file.  An external file is the best approach.},
%}




\newglossaryentry{Linux}
{
  name=Linux,
  description={is a generic term referring to the family of Unix-like
               computer operating systems that use the Linux kernel},
  plural=Linuces
}

\newglossaryentry{DOM1}
{
  name=DOM Level 1,
  description={The DOM Level 1 specification is separated into two parts: Core and HTML. The Core DOM Level 1 section provides a low-level set of fundamental interfaces that can represent any structured document, as well as defining extended interfaces for representing an XML document.}
}

\newglossaryentry{Apache}
{
  name=Apache,
  description={Open-source web server developed by the Apache Foundation.  One of the most widely used webservers on the planet.}
}

\newglossaryentry{JS}
{
  name=JavaScript,
  description={Scripting Language often included in web pages.  Requires an interpreter in the browser.}
}



\newglossaryentry{MySQL}{name=MySQL,
description={database engine by Oracle}}


\newglossaryentry{PDO}{name=PDO,
description={php Data Objects.  A lightweight database abstraction layer for php}}

\newglossaryentry{zxing}{name=ZXing,
description={pronounced Zebra Crossing, ZXing is an open-source bar-code scanner project.  ZXing can read standard bar-codes and QR codes}}

\newglossaryentry{QR}{name=QR,
description={Quick Response Code. A form of two dimensional machine readable image similar to a traditional bar code}}


\newglossaryentry{JavaScript}{name=JavaScript,
description={An interpreted computer language in widespread use in web applications}}


\newglossaryentry{php}{name=php,
description={php Hypertext Preprocessor. An interpreted computer language in widespread use on web servers}}



\newglossaryentry{Android}{name=Android,
description={A Linux based operating system for Smartphones and tablet computers}}



\newglossaryentry{ProGuard}{name=ProGuard,
description={A tool for optimizing and obfuscating compiled Android Apps}}
